Characterization of gaps in directly bonded Si compound optics

### 2014-10-22 AO_bondedSi.tex
closes #23 - cut Table 4, which was the interpretation of diversity of IR spectra

\begin{table}[h!]
  \caption{Interpretation of the diversity of IR spectra \label{tabInterpretation}}
  \begin{center}
    \begin{tabular}{ |p{8cm}| p{8cm} | p{2.2cm} |}
    \hline
    Appearance of spectra & Interpretation & Exemplars \\
    \hline
    Measurement within the prediction band & Life is good & VS21-M1, Figure \ref{VS21specm1}, VG15, VG07\\
    \hline
    Measured spectrum below the prediction band but shape is similar & Gap was slightly larger than predicted or bonding was incomplete& VS21-F1, Figure \ref{VS21specf1}, VS09, VG15, \\
    \hline
    Measured spectrum above the prediction band but shape is similar & Gap was slightly smaller than predicted & VS21-M2\\
    \hline
    Measured spectrum exceeds DSP reference puck & unanticipated anti-reflection coating on the surface of the Si sample (e.g. Sharpie marker residue) & VG08\\
    \hline
    High frequency, low amplitude wiggles superimposed upon smooth underlying trend & Large, unanticipated gap, with a small fill factor  & VS21-C3\\   
     																			     & wavelength dependent diffraction from the mesh patterns & VS21-C3\\       
     																			     & measurement artifact  & VS21-C3\\       												
    \hline
    Non-unit transmission constant with wavelength (gray spectrum) & Artifact of measurement- vignetting of beam, absorptive coating, zero-point drift & VS21-C4 \\
    \hline
    Completely different spectrum than anticipated with low absolute transmission & Large, inhomogeneous gap consistent with an IR bubble & VG09 \\
    \hline
    \end{tabular}
  \end{center}
\end{table}

@@

\subsection{Mitigation of measurement artifacts}
The principle artifacts and their interpretation are listed in Table \ref{tabInterpretation}.  We mitigated the artifacts in the following ways.  For the Sharpie marker behaving as an anti-reflection (AR) coating, we simply removed the sharpie with IPA.  We have mostly been able to rule out wavelength-dependent diffraction from the mesh pattern as a measurement artifact, since the beam size is large and the angular spread of diffraction from the mesh pattern would be much smaller than the spread of the beam.  Still, to remove this concern, we moved to using the coarse mesh rather than the medium or fine meshes, when possible.  We saw no difference in the bond quality surrounding the medium or fine meshes, which is consistent with results from the literature \cite{1992JEMat..21..669M}.  Specifically, the gas pressure of bonded wafers grows as the fill factor of gaps decreased.  In other words, what matters is the fill factor of gaps, not their relative sizes.  Since the fine, medium, and coarse meshes had the same fill factors, we anticipate no difference in the pressure of the gaps, and therefore no difference in the bonding properties.

>>>>

@@

\subsection{Mitigation of measurement artifacts}
We mitigated measurement artifacts in the following ways.  For the Sharpie marker behaving as an anti-reflection (AR) coating, we simply removed the sharpie with IPA.  We have mostly been able to rule out wavelength-dependent diffraction from the mesh pattern as a measurement artifact, since the beam size is large and the angular spread of diffraction from the mesh pattern would be much smaller than the spread of the beam.  Still, to remove this concern, we moved to using the coarse mesh rather than the medium or fine meshes, when possible.  We saw no difference in the bond quality surrounding the medium or fine meshes, which is consistent with results from the literature \cite{1992JEMat..21..669M}.  Specifically, the gas pressure of bonded wafers grows as the fill factor of gaps decreased.  In other words, what matters is the fill factor of gaps, not their relative sizes.  Since the fine, medium, and coarse meshes had the same fill factors, we anticipate no difference in the pressure of the gaps, and therefore no difference in the bonding properties.
